Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2020-09-29 manuscript/ERL_global_C_review.Rmd
update method to specify when models were not run

n_fluxes_with_ge7_areas <- table(ForC_biome_averages$Biome[idx_fluxes7])  
n_stocks_with_ge7_areas <- table(ForC_biome_averages$Biome[idx_stocks7]) #BREAKS HERE
n_fluxes_with_ge3_areas <- table(ForC_biome_averages$Biome[idx_fluxes3])  
n_stocks_with_ge3_areas <- table(ForC_biome_averages$Biome[idx_stocks3])  
```

@@

Of the `r nrow(ForC_measurements)` records in *ForC* v3.0, `r n_records` met our strict criteria for inclusion in this study (Fig. 1).
These records were distributed across `r n_plots_tot` plots in `r n_areas_tot` distinct geographic areas.
Of the 23 flux and 11 stock variables mapped in these diagrams, *ForC* contained sufficient mature forest data for inclusion in our statistical analyses (*i.e.*, records from $\ge$ 7 distinct geographic areas) for `r n_fluxes_with_ge7_areas[["Tropical broadleaf MATURE"]]` fluxes and `r n_stocks_with_ge7_areas[["Tropical broadleaf MATURE"]]` stocks in tropical broadleaf forests, `r n_fluxes_with_ge7_areas[["Temperate broadleaf MATURE"]]` fluxes and `r n_stocks_with_ge7_areas[["Temperate broadleaf MATURE"]]` stocks in temperate broadleaf forests, `r n_fluxes_with_ge7_areas[["Temperate conifer MATURE"]]` fluxes and `r n_stocks_with_ge7_areas[["Temperate conifer MATURE"]]` stocks in temperate conifer forests, and `r n_fluxes_with_ge7_areas[["Boreal conifer MATURE"]]` fluxes and `r n_stocks_with_ge7_areas[["Boreal conifer MATURE"]]` stocks in boreal forests.
For regrowth forests (<100 yrs), *ForC* contained sufficient data for inclusion in our statistical analyses (*i.e.*, records from $\ge$ **3** distinct geographic areas) for `r n_fluxes_with_ge3_areas[["Tropical broadleaf YOUNG"]]` fluxes and `r n_stocks_with_ge3_areas[["Tropical broadleaf YOUNG"]]` stocks in tropical broadleaf forests, `r n_fluxes_with_ge3_areas[["Temperate broadleaf YOUNG"]]` fluxes and `r n_stocks_with_ge3_areas[["Temperate broadleaf YOUNG"]]` stocks in temperate broadleaf forests, `r n_fluxes_with_ge3_areas[["Temperate conifer YOUNG"]]` fluxes and `r n_stocks_with_ge3_areas[["Temperate conifer YOUNG"]]` stocks in temperate conifer forests, and `r n_fluxes_with_ge3_areas[["Boreal conifer YOUNG"]]` fluxes and `r n_stocks_with_ge3_areas[["Boreal conifer YOUNG"]]` stocks in boreal forests.

>>>>

n_fluxes_with_ge7_areas <- table(ForC_biome_averages$Biome[idx_fluxes7])  
n_stocks_with_ge7_areas <- table(ForC_biome_averages$Biome[idx_stocks7])
n_fluxes_with_ge3_areas <- table(ForC_biome_averages$Biome[idx_fluxes3])  
n_stocks_with_ge3_areas <- table(ForC_biome_averages$Biome[idx_stocks3])  
```

@@

Of the `r nrow(ForC_measurements)` records in *ForC* v3.0, `r n_records` met our strict criteria for inclusion in this study (Fig. 1).
These records were distributed across `r n_plots_tot` plots in `r n_areas_tot` distinct geographic areas.
Of the 23 flux and 11 stock variables mapped in these diagrams, *ForC* contained sufficient mature forest data for inclusion in our statistical analyses (*i.e.*, records from $\ge$ 7 distinct geographic areas, and number of distinct plots < number of observations) for `r n_fluxes_with_ge7_areas[["Tropical broadleaf MATURE"]]` fluxes and `r n_stocks_with_ge7_areas[["Tropical broadleaf MATURE"]]` stocks in tropical broadleaf forests, `r n_fluxes_with_ge7_areas[["Temperate broadleaf MATURE"]]` fluxes and `r n_stocks_with_ge7_areas[["Temperate broadleaf MATURE"]]` stocks in temperate broadleaf forests, `r n_fluxes_with_ge7_areas[["Temperate conifer MATURE"]]` fluxes and `r n_stocks_with_ge7_areas[["Temperate conifer MATURE"]]` stocks in temperate conifer forests, and `r n_fluxes_with_ge7_areas[["Boreal conifer MATURE"]]` fluxes and `r n_stocks_with_ge7_areas[["Boreal conifer MATURE"]]` stocks in boreal forests.
For regrowth forests (<100 yrs), *ForC* contained sufficient data for inclusion in our statistical analyses (*i.e.*, records from $\ge$ **3** distinct geographic areas, and number of distinct plots < number of observations) for `r n_fluxes_with_ge3_areas[["Tropical broadleaf YOUNG"]]` fluxes and `r n_stocks_with_ge3_areas[["Tropical broadleaf YOUNG"]]` stocks in tropical broadleaf forests, `r n_fluxes_with_ge3_areas[["Temperate broadleaf YOUNG"]]` fluxes and `r n_stocks_with_ge3_areas[["Temperate broadleaf YOUNG"]]` stocks in temperate broadleaf forests, `r n_fluxes_with_ge3_areas[["Temperate conifer YOUNG"]]` fluxes and `r n_stocks_with_ge3_areas[["Temperate conifer YOUNG"]]` stocks in temperate conifer forests, and `r n_fluxes_with_ge3_areas[["Boreal conifer YOUNG"]]` fluxes and `r n_stocks_with_ge3_areas[["Boreal conifer YOUNG"]]` stocks in boreal forests.
